### 2017-04-11 paper/samplebody-journals.tex
pdf update

\quad Our  rst objective is to determine if certain attributes are indica- tive of business success. If we can find a way to predict whether or not a business will do well later on in its operation, that information will be useful to businesses looking to improve their model.

\quad Our second objective is to analyze the text of reviews for a sen- timent. The sentiment analysis will show the emotions conveyed by the reviewer as being pleased or angry at their experience with the business. Using the results of this analysis we hope to be able to determine if certain times of day, city locations, or other factors contribute to the experience of a customer. This information could also contribute to a business model. As an example, if certain loca- tions are more prone to angry customers it could indicate that the people in that area have high standards, the businesses are poorly run, or just that those customers tend to leave angry reviews.

\quad Our last objective is to  nd recurring problems in businesses. We will analyze review text to  nd the speci c issues that people are having with businesses. If a business has many reviews which all indicate a similar issue, then that is something a business owner would want to be aware of so that they can eliminate the problem.

@@

A previous winner, Hood et al., published a paper on assessing a business?s current rating/review state and future expectations with respect to review numbers on Yelp. The bulk of their work centered around the creation of additional features for the data (e.g. number of similar businesses within 1km, features of subsets of reviews such as average rating and number of unique users). From there they utilized various feature reduction and clustering techniques to build a prediction model. They were able to identify features that o ered greater accuracy in prediction of interest in the business (calculated as the predicted number of reviews within 6 months after a target date) as well as a create model for prediction that outperformed a basic linear regression.

@@

Huang et al. (2013) utilized probabilistic models to discover under- lying subtopics within Yelp reviews. This o ered a framework to categorize the reviews based on review text. From here, they were able to analyze the prevalence of various star ratings within each category. In this way, they could advise business owners as to the common trends among good and bad reviews that may not be ap- parent without considering the review text. McAuley and Leskovec built on this idea by combining such latent review topics with hidden rating driving factors, allowing them construct a rating prediction model.

@@

In one of the more in uential papers on the subject, Michael Luca showed a correlation between Yelp rating and revenue, highlighting the fact that rounding to half stars could signi cantly impact two similarly-rated restaurants if their averages fell on either side of the divide (e.g. 3.24 and 3.26). He goes on to build a model of market response based on review volume as well as the impact of user expertise. He concluded that such responses are consistent with a Bayesian learning model.

@@

The dataset has many optional attributes. There is an attribute called 'attributes' that is a list of optional attributes. The dataset is inconsistent and cannot be relied upon for each business. For instance, one of these attributes is ?Bike Parking?. This attribute is either true, false, or nonexistent. Speci cally the fact that this attribute might not be available for multiple businesses makes it unreliable.

\quad In addition, the data is not only restaurants but any kind of busi- ness. As a result they have another piece of data which is the cat- egories list. For each business this attribute attempts to classify the business. However some categories are extremely broad and the same type of business can be described in di erent ways. One example is that there is a bakery, but it?s also categorized as food. Many businesses will sell food, but the category of food will not be in their list of categories and instead it will be  lled with more speci c categories like Italian food.

@@

\quad The Yelp dataset contains up to one million di erent attributes about businesses from 11 di erent cities in 4 countries. The majority of these attributes will be unnecessary so there will be a large e ort in data reduction. For instance there are photographs included, but our questions does not require image analysis. There also attributes such as postal codes that are unnecessary because latitude and longitude is more accurate.

@@

\begin{itemize}
	\item{4.1 million reviews}
	\begin{verbatim}
	"review_id":(encrypted review id),
	"user_id":(encrypted user id),
	"business_id":(encrypted business id)"
	"stars":(star rating, rounded to half-stars),
	"date":(date, formatted: YYYY-MM-DD),
	"text":"review text",
	"useful":('useful' vote count),
	"funny":('funny' vote count),
	"cool": ('cool' vote count),
	"type": "review"
	\end{verbatim}
	\item{Informationon144,000businessesin11citiesfrom4coun- tries (incl. the US, Germany, Canada, and the U.K. (with 1.1 million business attributes)}
	\begin{verbatim}
	"business_id":(encrypted business id),
	"name":"business name",
	"neighborhood": "hood name",
	"address":"full address",
	"city":"city",
	"state":"state"(if applicable),
	"postal code":"postal code",
	"latitude":latitude,
	"longitude":longitude,
	"stars":(star rating, rounded to half-stars),
	"review_count":(number of reviews),
	"is_open":0/1 (closed/open),
	"attributes":[(localized attribute tags)],
	"categories":[(localized category names)],
	"hours":[(hours strings)],
	"type": "business"
	\end{verbatim}
	\item{Over 1M users}
	\begin{verbatim}
	"user_id":(encrypted user id),
	"name":"first name",
	"review_count":(number of reviews),
	"yelping_since": (date, formatted: YYYY-MM-DD),
	"friends":[(encrypted user ids)],
	"useful":('useful' vote count sent by user),
	"funny":('funny' vote count sent by user),
	"cool": ('cool' vote count sent by user),
	"fans":"number of fans the user has",
	"elite":["an array of years the user was elite"],
	"average_stars":floating point average like 4.31,
	"compliment_type": (compliment count),
		...(same for each compliment type)...
	"type":"user"
	\end{verbatim}
	\item{Over 200,000 user-submitted photographs, 947,000 tips, and aggregated check-in data}
\end{itemize}

@@

\quad The tools and methods used for this project will include a database for storing and integrating the data, libraries and modules for cleaning and preprocessing, and various tools for transformation, mining, pattern evaluation, and knowledge presentation. Given the json-formatted data, we've opted for using a NoSQL database like MongoDB or Cassandra. Fortunately, there are a number of options, considering our educational status, that will allow large storage volume as well as low latency read/write access. Hosting in such a manner will requireA number of Python libraries like Dora and FTFY (?fixes text for you?) intended for data cleaning and preprocessing will be used for these purposes. Yelp has already performed a substantial amount of cleaning on the data, so it is likely that minimal additional cleaning will be necessary, save for replacing missing values as mentioned above.

\quad Numpy and Scipy will be used to transform and mine the data, and other Python modules like Seaborn and Plotly (a Python API for D3) will be used for knowledge visualization and presentation. Finding angry reviews and recurring problems will make heavy use of NLP, so the team will rely on tools like Weka, the Text Analytics API from Microsoft Cognitive Services, and possibly some custom supervised text classi ers trained with the Facebook fastText pretrained word vectors to perform sentiment analysis on the review text.

@@

\section{Next Steps}

\quad Some major milestones before Spring Break (March 27th) will include organizing and integrating all the data in a relational database, as well as cleaning and preprocessing the data. After these steps have been completed, it will be much easier to begin preliminary investigations into our main questions for the project, such as reducing the entire set of attributes into just those that will be mined for each question. Milestones after Spring Break prior to April 11th will include using the tools listed above to answer two of our objective questions, while work after that will focus on answering the remaining question and writing the final report.

>>>>

\quad Our first objective is to determine if certain attributes are indicative of business success with respect to their average review rating (see sec. 2.3 for revenue relation). If we can find a way to predict whether or not a business will do well later on in its operation, that information will be useful to businesses looking to improve their model.

\quad Our second objective is to analyze the text of reviews for a sentiment. The sentiment analysis will show the emotions conveyed by the reviewer as being pleased or angry at their experience with the business. Using the results of this analysis we hope to be able to determine if certain times of day, city locations, or other factors contribute to the experience of a customer. This information could also contribute to a business model. As an example, if certain locations are more prone to angry customers it could indicate that the people in that area have high standards, the businesses are poorly run, or just that those customers tend to leave angry reviews.

\quad Our last objective is to find recurring problems in businesses. We will analyze review text to find the specific issues that people are having with businesses. If a business has many reviews which all indicate a similar issue, then that is something a business owner would want to be aware of so that they can eliminate the problem.

@@

A previous winner, Hood et al., published a paper on assessing a business?s current rating/review state and future expectations with respect to review numbers on Yelp. The bulk of their work centered around the creation of additional features for the data (e.g. number of similar businesses within 1km, features of subsets of reviews such as average rating and number of unique users). From there they utilized various feature reduction and clustering techniques to build a prediction model. They were able to identify features that offered greater accuracy in prediction of interest in the business (calculated as the predicted number of reviews within 6 months after a target date) as well as a create model for prediction that outperformed a basic linear regression.

@@

Huang et al. (2013) utilized probabilistic models to discover under- lying subtopics within Yelp reviews. This offered a framework to categorize the reviews based on review text. From here, they were able to analyze the prevalence of various star ratings within each category. In this way, they could advise business owners as to the common trends among good and bad reviews that may not be apparent without considering the review text. McAuley and Leskovec built on this idea by combining such latent review topics with hidden rating driving factors, allowing them construct a rating prediction model.

@@

In one of the more influential papers on the subject, Michael Luca showed a correlation between Yelp rating and revenue, highlighting the fact that rounding to half stars could significantly impact two similarly-rated restaurants if their averages fell on either side of the divide (e.g. 3.24 and 3.26). He goes on to build a model of market response based on review volume as well as the impact of user expertise. He concluded that such responses are consistent with a Bayesian learning model.

@@

The dataset has many optional attributes. There is an attribute called 'attributes' that is a list of optional attributes. The dataset is inconsistent and cannot be relied upon for each business. For instance, one of these attributes is 'Bike Parking'. This attribute is either true, false, or nonexistent. Speciifcally the fact that this attribute might not be available for multiple businesses makes it unreliable.

\quad In addition, the data is not only restaurants but any kind of business. As a result they have another piece of data which is the categories list. For each business this attribute attempts to classify the business. However some categories are extremely broad and the same type of business can be described in different ways. One example is that there is a bakery, but it?s also categorized as food. Many businesses will sell food, but the category of food will not be in their list of categories and instead it will be labelled with more specific categories like Italian food.

@@

\quad The Yelp dataset contains up to one million different attributes about businesses from 11 different cities in 4 countries. The majority of these attributes will be unnecessary so there will be a large effort in data reduction. For instance there are photographs included, but our questions does not require image analysis. There also attributes such as postal codes that are unnecessary because latitude and longitude is more accurate.

@@

\begin{itemize}
	\item{4.1 million reviews}
	\begin{verbatim}
	"review_id":(encrypted review id),
	"user_id":(encrypted user id),
	"business_id":(encrypted business id)"
	"stars":(star rating, rounded to half-stars),
	"date":(date, formatted: YYYY-MM-DD),
	"text":"review text",
	"useful":('useful' vote count),
	"funny":('funny' vote count),
	"cool": ('cool' vote count),
	"type": "review"
	\end{verbatim}
	\item{Information on 144,000 businesses in 11 cities from 4 countries (incl. the US, Germany, Canada, and the U.K. (with 1.1 million business attributes)}
	\begin{verbatim}
	"business_id":(encrypted business id),
	"name":"business name",
	"neighborhood": "hood name",
	"address":"full address",
	"city":"city",
	"state":"state"(if applicable),
	"postal code":"postal code",
	"latitude":latitude,
	"longitude":longitude,
	"stars":(star rating, rounded to half-stars),
	"review_count":(number of reviews),
	"is_open":0/1 (closed/open),
	"attributes":[(localized attribute tags)],
	"categories":[(localized category names)],
	"hours":[(hours strings)],
	"type": "business"
	\end{verbatim}
	\item{Over 1M users}
	\begin{verbatim}
	"user_id":(encrypted user id),
	"name":"first name",
	"review_count":(number of reviews),
	"yelping_since": (date, formatted: YYYY-MM-DD),
	"friends":[(encrypted user ids)],
	"useful":('useful' vote count sent by user),
	"funny":('funny' vote count sent by user),
	"cool": ('cool' vote count sent by user),
	"fans":"number of fans the user has",
	"elite":["an array of years the user was elite"],
	"average_stars":floating point average like 4.31,
	"compliment_type": (compliment count),
		...(same for each compliment type)...
	"type":"user"
	\end{verbatim}
	\item{Over 200,000 user-submitted photographs, 947,000 tips, and aggregated check-in data}
\end{itemize}

@@

\quad The tools and methods used for this project will include a database for storing and integrating the data, libraries and modules for cleaning and preprocessing, and various tools for transformation, mining, pattern evaluation, and knowledge presentation. Given the json-formatted data, we've opted for using a NoSQL database like MongoDB or Cassandra. Fortunately, there are a number of options, considering our educational status, that will allow large storage volume as well as low latency read/write access. Hosting in such a manner will require a number of Python libraries like Dora and FTFY ('fixes text for you') intended for data cleaning and preprocessing will be used for these purposes. Yelp has already performed a substantial amount of cleaning on the data, so it is likely that minimal additional cleaning will be necessary, save for replacing missing values as mentioned above.

\quad

\quad Numpy and Scipy will be used to transform and mine the data, and other Python modules like Seaborn and Plotly (a Python API for D3) will be used for knowledge visualization and presentation. Finding angry reviews and recurring problems will make heavy use of NLP, so the team will rely on tools like Weka, the Text Analytics API from Microsoft Cognitive Services, and possibly some custom supervised text classifiers trained with the Facebook fastText pre-trained word vectors to perform sentiment analysis on the review text.

@@

\section{Progress}

\quad There have been several major changes to the project tools and methods. Initially we planned on using a relational database, but ran into a lot of trouble. The inconsistencies between the user and business data made it too difficult to successfully import it into the database, so instead we decided to import the data straight into Weka. However, the format of the JSON file did not allow a successful import into Weka.

\quad Next we tried to convert the JSON file into CSV format. Once again Weka had issues due to the mismatch in attributes for each business (some had more attributes while others had less).

\quad Instead we opted to use a different tool, RapidMiner. Like Weka, RapidMiner incorporates a extensive machine learning functionality like classification, regression, clustering, and association and frequent itemset mining. RapidMiner is commercial software, but an educational version is available that removes limitations on the free version like only being able to process 10,000 rows at a time. Additionally, RapidMiner is more compatible with the missing data in our dataset and automatically corrects the formatting issues we had when attempting to use Weka. It does not support JSON so we reused the conversion code (found on the team GitHub as convert.py) to convert the data files to CSV.

\section{Results}

\subsection{Businesses}

\quad After importing the CSV formatted version of the data we tested some basic visualization of the data. For instance, in Figure 1 we created a histogram of the average star for a business versus the state in which it?s located. Basic graphs like these help refine our question. For example, why does Illinois have significantly lower average stars than others?

\quad The most pervasive issue with our business data is that many entries are missing data, most notably the 'attributes' and address information. Since these values are managed by the account owner, they vary widely across the businesses.

\begin{figure}[h]
\includegraphics[width=0.75\textwidth, center]{b_rating_by_state}
\end{figure}

\subsection{Users}

\quad There are some very interesting features here. It essentially provides a window into users' status, connections, and interaction within the Yelp ecosystem.

\begin{figure}[!h]
\includegraphics[width=0.45\textwidth, center]{u_reviews_vs_stars}
\end{figure}

\quad
\section{Next Steps}

\quad It is still necessary to reduce dimensionality. We?ve currently been working on the whole dataset and simply ignoring all attributes that fall in the category ?other.? This is cumbersome and it will become increasingly detrimental as we use more advanced techniques like clustering. The most prioritized attribute is the attributes portion. This attribute has the most issues because it is a miscellaneous catch-all where any attribute that didn?t fit with the others is thrown in. The issue is that it totally lacks consistency in the number and types of miscellaneous attributes included for each business. One business may have a Free Wifi attribute while others may not. After looking through the data it was clear that there wasn?t one attribute in this misc. category that was reliably present for all businesses. Although we have moved on to work with the other attributes, this one still needs work to decide if it should be omitted completely or if default values should be set instead.

\quad In addition, we need to combine the businesses and reviews dataset. This becomes extremely useful when examining the sentiment of a review and finding a correlation with the attributes of a business. This helps us build a model to potentially predict if a business receives negative or positive reviews based on its attributes.

\quad As mentioned before, we will be interested in clustering businesses together as to whether they receive positive or negative reviews based on their attributes. This can be difficult with the high number of dimensions of these datasets. We will try CLIQUE and PROCLUS for subspace clustering. PROCLUS will be particularly useful because the subspace for one business to qualify as ?positively reviewed? could be different than the subspace for another business. This allows us to process this data faster, but also consider the complexities of various subspaces.
